---
title: "scDown: A Pipeline for scRNASeq Downstream Analysis"
author: |
    | 
date: "`r format(Sys.Date(), '%m/%Y')`"
output: 
  rmarkdown::html_document:
    #theme: flatly
    highlight: pygments
    toc: true
    toc_depth: 3
    number_sections: true  ## if you want number sections at each table header
    df_print: paged
    #theme: united  # many options for theme, this one is my favorite.
#bibliography: library.bib
fig_width: 8 
fig_height: 5 
vignette: >
  %\VignetteIndexEntry{scDown_scProportionTest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width=8, 
  fig.height=5
)

```

## Introduction 
`scDown` is a robust pipeline for scRNASeq downstream analysis. This doscument provides a step-by-step guide to setting up and running `scDown` functions.

### Load Required Libraries 

```{r,message=FALSE,eval=FALSE}
library(scDown)
```

### Set Variables and Enviroment

Before running the pipeline, configure the following global variables. 

```{r, message=FALSE,eval=FALSE}
# Define output directory for results
output_dir <- "."

# Load Seurat object
seurat_obj_path <- system.file("extdata", "10X43_1_spliced_unspliced.rds", package="scDown")
seurat_obj <- readRDS(seurat_obj_path)

# Metadata cell type column
annotation_column <- "clusters"

```

### Convert H5AD File to Seurat Object
If you have `.h5ad` file, convert it to Seurat object using: 
```{r, message=FALSE,eval=FALSE}
h5ad_file <- "path/to/h5ad.file"
seurat_obj <- h5adToSeurat(h5ad_file, annotation_column=NULL)
```

Once the Seurat object and global Parmesans are set up, you can run scDown functions.

## Run scDown:run_scproportion

For more details on `scDown:run_scproportion`, please visit the following link:

<a href="scProportionTest.html" target="_blank">Run scDown:run_scproportion</a>

## Run scDown:run_cellchatV2

For more details on `cDown:run_cellchatV2`, please visit the following link:

<a href="scDown_CellChatV2.html" target="_blank">Run cDown:run_cellchatV2</a>

## Run scDown:run_monocle3

For more details on `scDown:run_monocle3`, please visit the following link:

<a href="scDown_monocle.html" target="_blank">Run scDown:run_monocle3</a>

## Run scDown:run_scvelo_full

For more details on `scDown:run_scvelo_full`, please visit the following link:

<a href="run_scvelo_full.html" target="_blank">Run scDown:run_scvelo_full</a>

