---
title: "scDown: A Pipeline for scRNASeq Downstream Analysis"
author: |
    | 
date: "`r format(Sys.Date(), '%m/%Y')`"
output: 
  rmarkdown::html_document:
    #theme: flatly
    highlight: pygments
    toc: true
    toc_depth: 3
    number_sections: false  ## if you want number sections at each table header
    df_print: paged
    #theme: united  # many options for theme, this one is my favorite.
#bibliography: library.bib
fig_width: 8 
fig_height: 5 
vignette: >
  %\VignetteIndexEntry{scDown_scProportionTest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width=8, 
  fig.height=5
)

```

#### Introduction 
`scDown` is a modular and user-friendly pipeline for downstream analysis of single-cell RNA sequencing (scRNA-seq) data. It streamlines complex analysis into simple, reproducible workflows. This vignette provides a step-by-step guide for setting up your environment and running key `scDown` functions.

Key Modules:

  1. scDown::run_scproportion: Compare cell-type proportions across conditions.
  
  2. scDown::run_cellchatV2: Infer and visualize cell-cell communication networks.
  
  3. scDown::run_monocle3: Perform Pseudotime trajectory inference.
  
  4. scDown::run_scvelo: Conduct RNA velocity analysis.

#### Load Required Libraries 

```{r,message=FALSE,eval=FALSE}
library(scDown)
```

#### Set Variables and Enviroment

Before running the pipeline, configure the following global variables, set the output directory to save the output results, and load Seurat object of single-cell RNA-seq data. The metadata column (annotation_column) is defined to specify the cell type or other annotation labels, ensuring the analysis runs with the correct input data.

```{r, message=FALSE,eval=FALSE}
# Define output directory for results
output_dir <- "/path/to/save/results"

# Load Seurat object
seurat_obj_path <- system.file("extdata", "10X43_1_spliced_unspliced.rds", package="scDown")
seurat_obj <- readRDS(seurat_obj_path)

# Metadata cell type column
annotation_column <- "clusters"

# Define the species: either "mouse" or "human"
species <- "mouse"

```

#### Convert H5AD File to Seurat Object
If you have `.h5ad` file, convert it to Seurat object using: 
```{r, message=FALSE,eval=FALSE}
h5ad_file <- "path/to/h5ad.file"
seurat_obj <- h5adToSeurat(h5ad_file, annotation_column=NULL)
```

Once the Seurat object and global Parmesans are set up, you can run scDown functions.

#### Run scDown:run_scproportion
Compare relative cell-type proportions across two biological conditions. 

➡️ <a href="scProportionTest.html" target="_blank">Read the tutorial</a>

#### Run scDown:run_cellchatV2
Explore cell–cell communication across cell types, tissues, or disease states.

➡️ <a href="scDown_CellChatV2.html" target="_blank">View full documentation</a>

#### Run scDown:run_monocle3
Perform pseudotime trajectory analysis and identify key regulators of cell state transitions.

➡️ <a href="scDown_monocle.html" target="_blank">Explore the pseudotime workflow</a>

#### Run scDown:run_scvelo
Predict future cell states and lineage relationships using RNA velocity and PAGA.

➡️ <a href="run_scvelo.html" target="_blank">Learn more</a>

➡️ <a href="run_scvelo_full.html" target="_blank">Run full pipeline</a>


